Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-08 MDPI_submission.Rmd
Commit 2023-11-08 19:09

authorcontributions: |
  For research articles with several authors, a short paragraph specifying their
  individual contributions must be provided. The following statements should be
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.

>>>>

# authorcontributions: |
#   For research articles with several authors, a short paragraph specifying their
#   individual contributions must be provided. The following statements should be
#   used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the
#   experiments; X.X. and Y.Y. analyzed the data; W.W. contributed
#   reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
#   limited to those who have contributed substantially to the work reported.
